A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-18 04_Severity_MetaAnalysis.Rmd
Logit transformed severity attempt

# predict values for dataset
new_sev <- predict(object =  g1, 
                   newdata = data.frame(y = PM_dat_D[,"PM_final_severity"])
                   )
# inspect distribution
hist(new_sev)
PM_dat_D$yi_percent <- new_sev

@@

# scale to 100% 
PM_dat_D$yi_percent  <- PM_dat_D$yi_percent * 100
PM_dat_D$vi_percent  <- PM_dat_D$vi_percent * 100

@@

# transform variance as per Paul et. al 2007
PM_dat_D <- 
   PM_dat_D %>%
   mutate(L_RR_v = vi *(1/replicates * (yi_percent ^ 2) + 1/replicates * (yi_Cp^2)))
```

@@

## Disease severity spray schedule meta-analysis  
First lets look at the results of the meta-analysis without transformation
```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mv <- rma.mv(
   yi = PM_final_severity,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)
summary(PMsev_mv)
```

@@

Finally lets assess the percent severity
```{r Metafor-Sev-analysis, cache=TRUE}
# remove controls for response ratio meta-analysis
dat_RR <- PM_dat_D[PM_dat_D$spray_management != "control",]

PMsev_mvPer <- rma.mv(
   yi = L_yi_p,
   V = L_RR_v,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = dat_RR
)

summary(PMsev_mvPer)
# Intecep <- coef(PMsev_mvPer)[1]
# ((coef(PMsev_mvPer)[2:6]+ Intecep)/100)* median(PM_dat_D$PM_final_severity) - (Intecep/100*median(PM_dat_D$PM_final_severity))
```
Model does not converge we will proceed with the square transformed severity

>>>>

# predict values for dataset
new_sev <- predict(object =  g1, 
                   newdata = data.frame(y = PM_dat_D[,"PM_final_severity"])
                   )
# one value is a negative, this should be a zero
new_sev[12] <- 0

# inspect distribution
hist(new_sev)
PM_dat_D$yi_percent <- new_sev

@@

@@

# transform variance as per Paul et. al 2007
PM_dat_D <- 
   PM_dat_D %>%
   mutate(L_RR_v = vi *(1/replicates * (yi_percent ^ 2) + 1/replicates * (yi_Cp^2)))

#logit transformed
PM_dat_D$yi_logit <- log(
   (PM_dat_D$yi_percent) / 
      (1 - (PM_dat_D$yi_percent))
   )
hist(PM_dat_D$yi_logit)
PM_dat_D$vi_logit <-
   (PM_dat_D$vi_percent) /
   (PM_dat_D$yi_percent * (1 - PM_dat_D$yi_percent)) ^ 2

# Correct -Inf to zeros
PM_dat_D[PM_dat_D$yi_logit == -Inf,"yi_logit"] <- 0.001
PM_dat_D[PM_dat_D$vi_logit == -Inf,"vi_logit"] <- 0.001
```

@@

## Disease severity spray schedule meta-analysis  
First lets look at the results of the meta-analysis without transformation
```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mv <- rma.mv(
   yi = PM_final_severity,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   #control = list(optimizer = "optim"),
   data = PM_dat_D
)
summary(PMsev_mv)
```

@@

Finally lets assess the percent severity
```{r Metafor-Sev-analysis, cache=TRUE}
# remove controls for response ratio meta-analysis
PMsev_mvPer <- rma.mv(
   yi = yi_logit,
   V = yi_logit,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

summary(PMsev_mvPer)

#summary(PMsev_mvPer)
# Intecep <- coef(PMsev_mvPer)[1]
# ((coef(PMsev_mvPer)[2:6]+ Intecep)/100)* median(PM_dat_D$PM_final_severity) - (Intecep/100*median(PM_dat_D$PM_final_severity))
```
Model does not converge we will proceed with the square transformed severity
```{r}
#logit transformed
PM_dat_D$yi_logit <- log(
   (PM_dat_D$yi_percent) / 
      (1 - (PM_dat_D$yi_percent))
   )

1- LaplacesDemon::invlogit(PMsev_mvPer$b)
mean(PM_dat_D[PM_dat_D$spray_management == "control","PM_final_severity"])
mean(PM_dat_D[PM_dat_D$spray_management == "Recommended_plus","PM_final_severity"])

```
